Boundary Labeling for annotated documents

### 2018-04-07 LaTeX/Paper.tex
Paper: Started Chapter 4 - Testing. Program: Added automatically generated R script for data visualisation. Misc: Updated .gitignore to disregard testing output.

\section{Data generation} %(Bin mit dem Titel unzufrieden, aber hier soll beschrieben werden, wie ich die einzelnen Testfälle erstellt habe.)

@@

@@

>>>>

\section{Data generation}

To generate data, we created our own texts using word length statistics from Table III in "Length-frequency statistics for written English" by Miller et al. \cite{Miller1958}, which lists word frequencies by length. We opted to use the data from the "Content Words" column, as the combined statistics almost exclusively produced words with three or less letters in our tests.
Using this data, we compiled our own fixed-length testing texts by creating words containing randomized alphabetic characters, taking care that the word length distribution matched our data.
Annotation sites are inserted into the text on either a normal or uniform distribution, and their labels contain similarly generated texts of randomized length.

To enable the inspection of individual texts, each text was generated from a randomized seed that is noted at time of creation.

@@

To generate many datasets at once, each testing run consists of 100 randomly generated texts that are routed one after the other without drawing them on-screen. During this process, we measure the time taken to complete each text, as well as the amount of successful routings, the total space used by all labels and the amount of P-Segments within the text area.
The results are saved to a CSV-style text file, and a R script is generated to visualize the data.

@@

%TODO:Run several tests with different parameters!
